\textbf{\sc Towards Deliberative Control in Marine Robotics}

### 2012-02-24 arch.tex
[arch] moved synch failure example earlier in the text [result] reword paragraph about gulper in order to enlarge the motivation from simply Gulper to "sensor based" missions
Made failure handling as a subsubsection

\begin{figure}[!htb]
  \centering
  \subfloat[\small A \rx agent is composed of multiple reactors or
    control loops (rounded boxes) which are connected through state
    variables provided by one reactor ({\color{blue}blue} solid line)
    with multiple possible clients ({\color{green}green} dashed
    lines)]{\includegraphics[scale=0.45]{figs/AUV-agent.pdf}
  \label{fig:agent}
  }
  \qquad
  \subfloat[\small State information flow between the \texttt{Pilot}
  and the \texttt{Vehicle} reactors in an \rx instance.  Observations
  transit as a bottom-up flow and apply to the execution frontier
  $\tau$.  Goal information flow from the top to the bottom and
  relates to desired future values of state variables.]{
    \includegraphics[width=0.4\columnwidth]{figs/TREX_flow}
    \label{fig:trex:flow}
  }
\caption{\small \rx reactors and shared state variables.}
\end{figure}

@@

\begin{figure}[!htbp]
  \centering
  \vskip-1pc
  \includegraphics[width=0.55\columnwidth]{figs/tick-cycle}
  \caption{\small \rx reactor execution cycle: {\em Deliberation} is
    interrupted by {\em synchronization} at the beginning of every
    {\em tick} allowing integration of state information.}
  \label{fig:tick-exec}
  \vskip-0.8pc
\end{figure}

@@

It is important to note that, in T-REX architecture, the only critical
task of a reactor is to successfully identify its state through
synchronization as the execution frontier advances. Indeed, a reactor
that fails to integrate its {\em external} state updates and/or
identify its {\em internal} state at any tick express that it is not
able anymore to explain the state of the world. In the agent point of
view that means that any state information from this reactor is not to
be trusted anymore and results on this reactor exclusion from the
execution cycle and consequent destruction. As the agent destroy 
the  faulty reactor is destroyed the agent produced on all of 
its former {\em internal} timelines the special observation 
\texttt{Failed} to all the reactors which did declare these state 
variables as {\em external} informing
them through this that this specific state variable is currently
unavailable. On the other hand all goals exchanged between reactors
are considered as rejectable by the reactor that manages them. As a
result the failure to find a plan for these goals, while to be avoided,
is not considered as a critical failure of the reactor and will only
result on these goals being ignored until new goals are received.

>>>>

\begin{figure}[t]
  \centering
  \subfloat[\small A \rx agent is composed of multiple reactors or
    control loops (rounded boxes) which are connected through state
    variables provided by one reactor ({\color{blue}blue} solid line)
    with multiple possible clients ({\color{green}green} dashed
    lines)]{\includegraphics[scale=0.45]{figs/AUV-agent.pdf}
  \label{fig:agent}
  }
  \qquad
  \subfloat[\small State information flow between the \texttt{Pilot}
  and the \texttt{Vehicle} reactors in an \rx instance.  Observations
  transit as a bottom-up flow and apply to the execution frontier
  $\tau$.  Goal information flow from the top to the bottom and
  relates to desired future values of state variables.]{
    \includegraphics[width=0.4\columnwidth]{figs/TREX_flow}
    \label{fig:trex:flow}
  }
\caption{\small \rx reactors and shared state variables.}
\end{figure}

@@

\label{sec:delib-exec-as}
\begin{figure}[!htbp]
  \centering
  \vskip-1pc
  \includegraphics[width=0.55\columnwidth]{figs/tick-cycle}
  \caption{\small \rx reactor execution cycle: {\em Deliberation} is
    interrupted by {\em synchronization} at the beginning of every
    {\em tick} allowing integration of state information.}
  \label{fig:tick-exec}
  \vskip-0.8pc
\end{figure}

@@

\subsubsection{Reactors failure handling in \rx}
\label{sec:rx-reactor-failure}
It is important to note that, in T-REX architecture, the only critical
task of a reactor is to successfully identify its state through
synchronization as the execution frontier advances. Indeed, a reactor
that fails to integrate its {\em external} state updates and/or
identify its {\em internal} state at any tick express that it is not
able anymore to explain the state of the world. In the agent point of
view that means that any state information from this reactor is not to
be trusted anymore and results on this reactor exclusion from the
execution cycle and consequent destruction. As the agent destroy 
the  faulty reactor is destroyed the agent produced on all of 
its former {\em internal} timelines the special observation 
\texttt{Failed} to all the reactors which did declare these state 
variables as {\em external} informing
them through this that this specific state variable is currently
unavailable. On the other hand all goals exchanged between reactors
are considered as rejectable by the reactor that manages them. As a
result the failure to find a plan for these goals, while to be avoided,
is not considered as a critical failure of the reactor and will only
result on these goals being ignored until new goals are received.
